Metadata control

### 2022-10-13 metadata/metadata_control.Rmd
Adding culture data to metadata

>>>>

## Culture data ----

```{r}
clean_stans <- read.csv(file = "made_data/clean_stans.csv")

culture_desc <- readxl::read_xlsx("raw_data/Heal_mSystems uncorrected Metabs_SuppTabs_20210223.xlsx",
                  sheet = "S7_Culturedescriptions_full")
culture_data <- readxl::read_xlsx("raw_data/Heal_mSystems uncorrected Metabs_SuppTabs_20210223.xlsx",
                                  sheet = "S5_FullEnviroCulture_PeakAreas")
taxa_metabs <- culture_data %>%
  filter(!str_detect(MassFeature_Column, "RP$")) %>%
  mutate(polarity=tolower(str_extract(MassFeature_Column, "Neg$|Pos$"))) %>%
  select(Identification, polarity, `7803_B`:Nmar_3) %>%
  pivot_longer(cols = `7803_B`:Nmar_3) %>%
  left_join(clean_stans %>% select(compound_name, compound_name_old, polarity), 
            by=c(Identification="compound_name_old", "polarity")) %>%
  filter(!is.na(compound_name)) %>%
  left_join(culture_desc %>% select(name=`Sample ID`, taxa=`Broad taxon`, species=Species),
            by="name") %>%
  filter(!is.na(value)) %>%
  select(compound_name, polarity, broad_taxa=taxa, species, id=name, value)

write.csv(taxa_metabs, file = "made_data/taxa_metabs.csv")
```
